The Calibration Reference Data System

### 2015-10-06 docs/paper/crds.tex
adding references, fixing text refernces, etc, adding draft watermark...
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2129 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

\lstset{
  basicstyle=\ttfamily,
  showstringspaces=false,
  stringstyle=\color{red},
  morecomment=[l]{/},
  commentstyle=\color{blue},
}

@@

In the context of HST (see section xxx), reversion to prior sets of 
rules has been used to
support pipeline regression testing and coordinate CRDS with available
historical system states of the rest of the pipeline.

@@

Figure~\ref{fig:batchsubmission} shows the starting page for submitting
a batch set of files using the streamlined system.

Figure~\ref{fig:goodsubmissionreview} shows the results of a successfully validated batch  submission request.

Figure~\ref{fig:failedsubmission} shows the results of an unsuccessfully validated batch submission request showing what went wrong.

Figure~\ref{fig:confirmedsubmission} shows the results of a successfully completed submission request.

@@

The user identifies the local files designated as the files to replace existing
ones. When all the updates have been identified, the submit button [or
whatever] is clicked, and CRDS will then validate each of the reference
files. If they all pass validation, the user will be presented the results of
the results that will be produced (e.g., the new filenames for the reference
files, rmaps and context files, and other summary information). An example of a
successful validation is shown in Figure xxx. At this point the user confirms
the submission after which they will be assigned unique names, added to the
CRDS database of reference files, sent to the STScI archive for archiving, and
placed in the disk-based repository of reference files. If the validation
doesn't pass, the results indicate what the problem is so the user may make the
necessary corrections. Figure xxx shows such a summary of problems.

@@

This is handled by using the tools that the JWST pipeline use to validate the
reference files. These are based on data models that use JSON Schema (ref xxx)
to define the mandatory aspects of the data expected, including all the
expected data elements (whether arrays or tables), the allowable dimensionality
and datatype, and required metadata.

@@

\item other cases? xxx
\end{enumerate}

@@

Reference files in FITS, JSON, and ASDF format are supported.

@@

\section{Use for HST}

@@

This work was supported by the JWST mission, a joint effort of NASA,
ESA, and CSA. STScI is operated on behalf of NASA by the Association
of Universities for Research in Astronomy, and by the HST mission xxx
The implementation was aided by
Jonathan Eisenhamer, and the integration into the operations system by Michael
Swam. Testing from the instrument scientist perspective was carried out by Rosa
Diaz and Matthew McMaster. Motivations for the work were provided by the weekly
Science Software Branch Donut meeting.

>>>>

\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}
\lstset{
  basicstyle=\ttfamily,
  showstringspaces=false,
  stringstyle=\color{red},
  morecomment=[l]{/},
  commentstyle=\color{blue},
}

@@

In the context of HST (see section~\ref{sec:HST}), reversion to prior sets of 
rules has been used to
support pipeline regression testing and coordinate CRDS with available
historical system states of the rest of the pipeline.

@@

@@

The authenticated user begains a batch submission of files on the batch
submission page (Figure~\ref{fig:batchsubmission}) 
by identifying the local files designated as the 
files to replace existing ones (note, the local file names are not the 
names the files will have when ingested into CRDS). 
When all the updates have been identified, the submit button [or
whatever] is clicked, and CRDS will then validate each of the reference
files. If they all pass validation, the user will be presented the results of
the results that will be produced (e.g., the new filenames for the reference
files, rmaps and context files, and other summary information). An example of a
successful validation is shown in Figure~\ref{fig:goodsubmissionreview}.
At this point the user confirms
the submission after which they will be assigned unique names, added to the
CRDS database of reference files, sent to the STScI archive for archiving, and
placed in the disk-based repository of reference files. When the submission
process completes, the user is presented with a summary page, shown in
Figure~\ref{confirmedsubmission}

If the validation
doesn't pass, the results indicate what the problem is so the user may make the
necessary corrections. Figure~\ref{fig:failedsubmission}
shows such a summary of problems.

@@

This is handled by using the tools that the JWST pipeline use to validate the
reference files. These are based on data models that use JSON Schema
(\citealt{JSONSchemaCore, JSONSchemaValidation, JSONHyperSchema, JSONSchemaGuide})
to define the mandatory aspects of the data expected, including all the
expected data elements (whether arrays or tables), the allowable dimensionality
and datatype, and required metadata.

@@

\end{enumerate}

@@

Reference files in FITS 
(\citealt{2010FITS}), JSON (\citealt{JSON}), and ASDF (\citealt{2015ASDF})
format are supported.

@@

\section{Use for HST}
\label{sec:HST}

@@

This work was supported by the JWST mission, a joint effort of NASA,
ESA, and CSA. STScI is operated on behalf of NASA by the Association
of Universities for Research in Astronomy, and by the HST mission xxx
The implementation was aided by
Jonathan Eisenhamer, and the integration into the operations system by Michael
Swam. Testing from the instrument scientist perspective was carried out by Rosa
Diaz and Matthew McMaster.
